---
title: "References"
author: "Spring 2017 - Master's Research Project Team"
date: "February 15, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(knitcitations)
library(RefManageR)


cleanbib()

cite_options(style="markdown")

```

```{r bib-data, echo=FALSE}
bibMicroCalDL <- bibentry(bibtype="Misc",
                 author=personList(person(family="Wang", given="Jinhua"),
                                   person(family="Yang", given="Xi"),
                                   person(family="Cai", given="Hongmin"),
                                   person(family="Tan", given="Wanchang"),
                                   person(family="Jin", given="Cangzheng"),
                                   person(family="Li", given="Li")),
                 publisher="Scientific Reports",
                 title="Discrimination of Breast Cancer with Microcalcifications on Mammography by Deep Learning",
                 year=2016,
                 doi = "10.1038/srep27327",
                 note="Accessed: Feb 7, 2017",
                 url="http://www.nature.com/articles/srep27327")

bibMIAS <- bibentry(bibtype="Misc",
                 author=personList(person(family="Suckling", given="J")),
                 publisher="Mammographic Image Analysis Society",
                 title="The Mammographic Image Analysis Society Digital Mammogram Database",
                 year=1994,
                 note="Accessed: Feb 9, 2017",
                 url="http://peipa.essex.ac.uk/info/mias.html")

bibDDSM <- bibentry(bibtype="Misc",
                     author=personList(person(family="Heath", given="M"),
                                       person(family="Bowyer", given="K"),
                                       person(family="Kopans", given="D"),
                                       person(family="Kegelmeyer", given="W.P."),
                                       person(family="Moore", given="R")),
                     publisher="Medical Physics Publishing",
                     title="The Digital Database for Screening Mammography",
                     note="Accessed: Feb 12, 2017",
                     year=2001,
                     url="http://marathon.csee.usf.edu/Mammography/Database.html")

bibHeathSw <- bibentry(bibtype="Misc",
                     author=personList(person(family="Heath", given="M")),
                     publisher="Computer Vision Laboratory, University of South Florida",
                     title="Mammography Software",
                     note="Accessed: Feb 12, 2017",
                     year=2000,
                     url="http://marathon.csee.usf.edu/Mammography/software/heathusf_v1.1.0.html")

bibDDSMUtility <- bibentry(bibtype="Misc",
                           author=personList(person(family="Sharma", given="Anmol")),
                           publisher="GitHub",
                           title="DDSM Utility",
                           journal="GitHub repository",
                           year=2015,
                           url="https://github.com/trane293/DDSMUtility")
```

# Overview

Inorder for the references to appear in the References section, they much be "cited". Normally, these citations would appear within the normal flow of the paper, but for our purposes in this document, we can just cite them below as bullets to force the rendering in the References section.

* Discrimination of Breast Cancer with Microcalcifications on Mammography by Deep Learning `r citep(bibMicroCalDL)`
* The Mammographic Image Analysis Society Digital Mammogram Database `r citep(bibMIAS)`
* DDSM: Digital Database for Screening Mammography `r citep(bibDDSM) `
* Mammography Software `r citep(bibHeathSw)`.
* DDSM Utility `r citep(bibDDSMUtility)`.

# References

```{r bib-references, results='asis', echo=FALSE, message=FALSE}
BibOptions(style="html", bib.style="authortitle")
bibliography()
```